% Options for packages loaded elsewhere
% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}
\usepackage{xcolor}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother


\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother


% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}



\setlength{\emergencystretch}{3em} % prevent overfull lines

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}



 


\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Klippel-Trenaunay Syndrome complicated by Kasabach-Merritt syndrome during pregnancy},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}


\title{Klippel-Trenaunay Syndrome complicated by Kasabach-Merritt
syndrome during pregnancy}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{A case report and review of the literature}
\author{}
\date{}
\begin{document}
\maketitle


\section{Authors}\label{authors}

Mourad Elfaham\textsuperscript{1}, Aya Attia\textsuperscript{1}, Mohamed
Waheed\textsuperscript{1}, Mohamed Essam\textsuperscript{1}, Salma
Saad\textsuperscript{1}, Mariam Sarhan\textsuperscript{1}, Marwa
Mourad\textsuperscript{1}, Mohamed Hegazy\textsuperscript{1}, Farah
Said\textsuperscript{1}, Sarah Tarek\textsuperscript{1}, Amgad
Gamal\textsuperscript{1}, Sara Ibrahim Abdelkader\textsuperscript{2*},
Ahmed Azab\textsuperscript{2}, Mohammed Ghanem\textsuperscript{2}, Rahma
Alaa Abdelhafez\textsuperscript{2}, Nour Atif\textsuperscript{2}, Maha
Moemen\textsuperscript{2}, Belgin Ahmed Nagah\textsuperscript{2}, Ashraf
Nabhan\textsuperscript{1,3}

\section{Affiliation}\label{affiliation}

\textsuperscript{1} Faculty of Medicine, Ain Shams University, Cairo,
Egypt.

\textsuperscript{2} Faculty of Medicine, Galala University, Attaka,
Suez, Egypt.

\textsuperscript{3} Faculty of Medicine, MTI University, Cairo, Egypt.
01069663999

* Corresponding author: Sara Ibrahim Abdelkader. Faculty of Medicine,
Galala University, Attaka, Suez, Egypt. Email:
\href{mailto:sara.elzeftawy@gu.edu.eg}{\nolinkurl{sara.elzeftawy@gu.edu.eg}},
ORCID: \href{https://orcid.org/0009-0002-5877-4722}{0009-0002-5877-4722}

\textbf{Word count:} 2500

\section{Abstract}\label{abstract}

The co-occurrence of Klippel--Trenaunay syndrome and Kasabach-Merritt
syndrome in pregnancy is extremely rare and represents a critical
obstetric emergency with significant maternal and fetal risks, demanding
early recognition and immediate multidisciplinary intervention.

We report the case of a 28-year-old pregnant woman with known
Klippel--Trenaunay syndrome who developed Kasabach--Merritt phenomenon
during pregnancy. The fetus suffered severe growth restriction and
absent end-diastolic flow on umbilical artery Doppler. A cesarean
section was performed at 35 weeks of gestation.

This case highlights the complexity of managing pregnancy in women with
Klippel--Trenaunay syndrome complicated by Kasabach Merritt syndrome and
emphasizes the importance of multidisciplinary surveillance and timely
delivery.

\textbf{Keywords:} Klippel--Trenaunay syndrome; angioosteohypertrophy
syndrome; Kasabach Merritt syndrome; fetal growth restriction; high-risk
pregnancy

\section{Introduction}\label{introduction}

Klippel-Trenaunay syndrome (KTS) is a rare congenital disorder affecting
an estimated 2--5 per 100,000 individuals. Its features include a triad
of capillary malformations, venous and lymphatic anomalies, and limb
overgrowth. {[}1,2{]}

KTS was first described in 1900 as Naevus vasculosus osteohypertrophicus
by two French physicians, Maurice Klippel and Paul Trenaunay. It was
previously considered similar to the less common Parkes Weber syndrome
(PWS), distinguished from KTS by the presence of arteriovenous
malformations (AVMs), which is abnormal connections between arteries and
veins in the affected limb, potentially leading to high-output heart
failure. Despite this distinction, both conditions share similar
management principles.{[}3,4{]}. KTS is currently classified within the
PIK3CA-Related Overgrowth Spectrum (PROS), a group of overgrowth
syndromes with overlapping phenotypic features that share mutations in
the PIK3CA~gene.

When pregnancy occurs in the setting of KTS, it presents significant
challenges due to hormonally and hemodynamically driven vascular
engorgement, increasing the risk of thromboembolism, hemorrhage, and
coagulopathy. {[}5{]} Coagulopathy may reflect the development of
Kasabach-Merritt syndrome (KMS).

Even more rarely, Kasabach-Merritt Syndrome (KMS), first described in
1940, is a life-threatening consumptive coagulopathy associated with
rapidly proliferating vascular tumors such as kaposiform
hemangioendothelioma and tufted angioma, and can emerge or worsen during
pregnancy in women with KTS. KMS in pregnancy is exceedingly rare, but
when it occurs, it carries a historical mortality rate of 30--40\%,
driven by severe thrombocytopenia, hypofibrinogenemia, and disseminated
intravascular coagulation (DIC). {[}6{]}

The co-occurrence of KTS and KMS in pregnancy represents a critical
obstetric emergency, that demands early recognition and immediate
multidisciplinary intervention to reduce mortality. This convergence is
extremely rare and only three cases have been previously
reported.{[}7--9{]}.

This case report details the clinical course and successful management
of a pregnant woman with KTS complicated by acute KMS and fetal growth
restriction with abnormal umbilical artery Doppler findings. We
highlight the clinical challenges and management strategies and
underscores the importance of early recognition and coordinated care to
optimize maternal and neonatal outcomes.

\section{Case Presentation}\label{case-presentation}

A 28-year-old multigravida, P2CS+1 (1L) was first admitted at 30+1 weeks
of gestation for clinically significant hematuria on the 16th of
December in Ain Shams University Hospital, Egypt. The timeline is
detailed in Table~\ref{tbl-1}

The patient was first diagnosed at two years of age with
Klippel-Trenaunay syndrome (KTS) involving both lower limbs, back,
pelvis, and urinary bladder. She underwent surgery for varicose veins
seven years ago, as well as orthopedic surgery for the insertion of
plates and screws a year and a half ago.

Her obstetric history includes two cesarean sections. Her first
pregnancy was seven years ago and ended in neonatal death. Her second
pregnancy was complicated by severe preeclampsia, postpartum wound
hematoma, and sepsis, requiring ICU admission. She also had a history of
spontaneous miscarriage for which she did not undergo dilatation and
curettage. For her current pregnancy, she received two doses of
antenatal corticosteroids on December 14\textsuperscript{th} and
15\textsuperscript{th}.

On examination, her blood pressure was 120/80 mmHg, temperature was
36.2° C, and heart rate was 68 bpm. Port-wine stains were seen in the
back and gluteal region with discrepancy in the length of both lower
limbs.

A complete blood picture (CBC) revealed microcytic hypochromic anemia
(hemoglobin 7.0 g/dl, hematocrit 23.0\%) and thrombocytopenia (128,000
u/L), for which she received six units of packed cell transfusion to
correct the worsening hemoglobin. ABO and Rh typing indicated B positive
blood. Viral workup was negative for Hepatitis C and B and human
immunodeficiency virus (HIV).

Ultrasonography (US) demonstrated estimated fetal weight below the 10th
percentile consistent with intrauterine growth restriction (IUGR), and
an abnormal umbilical artery Doppler showing absent end-diastolic blood
flow.

Urological consultation was sought for the significant hematuria.
Initial management included intravenous tranexamic acid and insertion of
an indwelling silicone three-way urinary catheter for one week.

On December 18\textsuperscript{th}, pelviabdominal magnetic resonance
imaging (MRI) was performed, demonstrating a gravid uterus with a single
intrauterine pregnancy in cephalic lie with unremarkable placental
location and attachment. Compression of the left ovarian vein and the
left common iliac vein by the gravid uterus was seen, with associated
slowing and dilatation of both veins. Extensive dilated tubular tortuous
lesions suggestive of varicosities were observed in the pelvic,
perivesical, perineal, and gluteal regions, more prominent on the left
side, showing a ``bag of worms'' appearance. Similar lesions were
present in breast subcutaneous tissue bilaterally. The urinary bladder
contained blood products.\\
The liver was mildly enlarged with noticeable vascular compression,
while the gall bladder, spleen, and kidneys were unremarkable. Minimal
bilateral pleural effusion was noticed.

On December 21\textsuperscript{st}, pelviabdominal ultrasonography,
Color-Doppler study of both lower limb veins, and Color-Doppler and
duplex study of both lower limb arteries were performed.\\
Pelviabdominal ultrasonography revealed hepatosplenomegaly, soft tissue
lesions in the urinary bladder, bilateral refluxing parametrial venous
channels, and a single viable intra-uterine fetus.\\
Lower limb vessel studies showed a normal venous and arterial system,
with no evidence of deep vein thrombosis.

Serial CBCs showed improving hemoglobin over the four days following the
packed RBCs transfusion, which reached 9.4g/dL on December
22\textsuperscript{nd}, while platelet count remained persistently low
between 82,000 and 104,000. Iron profile showed elevated UIBC
(unsaturated iron binding capacity) and low transferrin saturation.
Lactate dehydrogenase (LDH) was elevated at 454 IU/L.\\
On the same day, urinalysis demonstrated hematuria (2+), pyuria, and
mild proteinuria (1+). Microscopic examination revealed \textgreater100
red blood cells per high power field (RBCs/HPF), 40-45 pus cells per
high power field (Pus Cell/HPF), and increased epithelial cells (2+).
Uric acid crystals were present (2+). Other parameters were within
normal limits.

Coagulation studies on December 27\textsuperscript{th} and
28\textsuperscript{th} showed slightly elevated Prothrombin time (PT)
while serum creatinine was low.

A contrast-enhanced pelvic MRI was done on January 1, showing extensive
venous malformations within the pelvis involving the cervix, vagina,
anal canal, and extending downwards to the perineum and both labias.
Extensive lesions were also seen within the gluteal region, thigh,
anterior part of the abdominal cavity, and intravesically.

The patient was monitored daily with regular assessment of vital
parameters, general condition, fetal kicks, vaginal bleeding, uterine
contractions, and evidence of membrane rupture. She received one unit of
packed RBCs on January 2, followed by an additional unit on January 5.~~

At 35 weeks of gestation, based on worsening fetal Doppler parameters
and maternal risks, a multidisciplinary team involving obstetrics,
hematology, anesthesia, and neonatology recommended delivery by
emergency cesarean section. Subsequently, on the 18\textsuperscript{th}
of January, a cesarean section was performed at 35 weeks of gestation
under general endotracheal anesthesia.\\
Vertical midline abdominal incision was made revealing significant
varicosities in the anterior abdominal wall, over the lower uterine
segment, and in the interface between the uterus and the bladder. Lower
segment incision of the uterus was made to deliver the fetus and
placenta. This was followed by closure of the uterine wall in two
layers. Placenta was complete, perineum intact. Hemostasis was secured
and no intraperitoneal drains were left. Only a subcutaneous drain was
inserted for seven days. The skin was closed by interrupted mattress
sutures.

A female neonate weighing 1900 g was delivered with Apgar scores of 7
and 9 at 1 and 5 minutes respectively. The neonate did not receive
vaccination due to low birth weight and did not require observation or
respiratory support.

Postoperatively, the mother was admitted to the intensive care unit
(ICU) due to hemoperitoneum. Her pharmacological therapy included
low-molecular-weight heparin (LMWH), tranexamic acid, ceftriaxone,
pantoprazole, intravenous paracetamol, and charcoal-based herbal

Slight hematuria was noted on the first post-operative day, and labs
showed a declining hemoglobin and platelet count, as well as markedly
elevated LDH, alkaline phosphatase, creatine kinase, and bilirubin. LMWH
therapy was thereby put on hold, and the patient was given packed red
blood cells and fresh frozen plasma, receiving a total of ten units of
packed cell transfusion and fresh frozen plasma (with a one-to-one
ratio) over the course of seven days. Additional laboratory
investigations are demonstrated in Table~\ref{tbl-2}

On the second post-operative day, the patient's hemoglobin and platelet
count rapidly deteriorated, decreasing from 9.6g/dl and 218,000 plt to
7.6g/dl and 104,000 plt respectively. Replacement with blood products
continued.

On post-operative day three, TVUS revealed marked hemoperitoneum with a
localized hematoma related to the lower uterine segment, approximately
12 cm in maximum length. A decision for conservative management was made
by the attending consultant and the head of the unit. Pharmacological
therapy was adjusted; LWMH was resumed, in addition to tranexamic acid,
1 amp calcium, 1 amp dexamethasone, magnesium sulfate, cefepime,
omeprazole, clindamycin, and intravenous paracetamol.

On post-operative day four, labs showed low fibrinogen (1.4g/l) and
significantly elevated D-dimer (35.200 ug/mlFEU). These findings were
suggestive of Kasabach Meritt Syndrome.

Urinalysis on day 6 demonstrated hematuria (2+), mild pyuria and mild
proteinuria (1+). Microscopic examination revealed \textgreater100 red
blood cells per high power field (RBCs/HPF), 13-15 pus cells per high
power field (Pus Cell/HPF), and increased epithelial cells (1+). On day
7, her hemoglobin stabilized at 10.1 g/dl and remained stable over the
following three days, while her platelet count remained low at 64,000.

After further stabilization, the patient was discharged on day ten
postoperatively. She was seen on day nineteen in the outpatient clinic.
General condition was fair, lax abdomen, and skin sutures were removed
with optimal healing of the abdominal incision.

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 2\tabcolsep) * \real{0.2791}}
  >{\raggedright\arraybackslash}p{(\linewidth - 2\tabcolsep) * \real{0.7209}}@{}}
\caption{Patient timeline}\label{tbl-1}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Date
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Timeline
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Date
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Timeline
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
30 +1 weeks' gestation (Dec 16, 2025) & Admission of a case of KTS,
presenting with hematuria; anemia and thrombocytopenia; fetus
\textless10th percentile, received tranexamic acid and 6 units PRBCs. \\
30+1 to 35 weeks' gestation (Dec 18, 2025 -- Jan 17, 2026) &
\begin{minipage}[t]{\linewidth}\raggedright
MRI: extensive venous malformations (pelvis, thigh, abdomen).\\
Close maternal/fetal monitoring.\\
Intermittent transfusions slight hemoglobin improvement; fluctuating
platelets; prolonged PT.\strut
\end{minipage} \\
35 weeks (Jan 18, 2026) & Emergency cesarean section for fetal
compromise → female neonate (1900 g). Mother addmitted to ICU,
hemoperitoneum managed conservatively. \\
Postoperative course & \textbf{Day 1:} Hematuria → LMWH discontinued;
transfusion support (total 10 units PRBC + FFP over 7 days)

\textbf{Day 2:} Hb 9.6→7.6 g/dL; platelets 218×10³→104×10³/µL

\textbf{Day 3:} Conservative management → LMWH resumed + tranexamic acid

\textbf{Day 4:} Hypofibrinogenemia (1.4 g/L) + elevated D-dimer (35.2
µg/mL) → consistent with Kasabach--Merritt syndrome

\textbf{Day 7:} Hb stabilized (10.1 g/dL); persistent thrombocytopenia
(64×10³/µL)

Day 10: Discharged in stable condition

\textbf{Day 19:} Outpatient follow-up: fair general condition; sutures
removed \\
\end{longtable}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 18\tabcolsep) * \real{0.1000}}
  >{\raggedright\arraybackslash}p{(\linewidth - 18\tabcolsep) * \real{0.1000}}
  >{\raggedright\arraybackslash}p{(\linewidth - 18\tabcolsep) * \real{0.1000}}
  >{\raggedright\arraybackslash}p{(\linewidth - 18\tabcolsep) * \real{0.1000}}
  >{\raggedright\arraybackslash}p{(\linewidth - 18\tabcolsep) * \real{0.1000}}
  >{\raggedright\arraybackslash}p{(\linewidth - 18\tabcolsep) * \real{0.1000}}
  >{\raggedright\arraybackslash}p{(\linewidth - 18\tabcolsep) * \real{0.1000}}
  >{\raggedright\arraybackslash}p{(\linewidth - 18\tabcolsep) * \real{0.1000}}
  >{\raggedright\arraybackslash}p{(\linewidth - 18\tabcolsep) * \real{0.1000}}
  >{\raggedright\arraybackslash}p{(\linewidth - 18\tabcolsep) * \real{0.1000}}@{}}
\caption{Relevant abnormal laboratory results throughout the clinical
course.}\label{tbl-2}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Parameters/Timing
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
December 16 (Day of admission)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
December 22
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
December 28
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
POD 1
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
POD 2
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
POD 4
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
POD 6
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
POD 7
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Reference range
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Parameters/Timing
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
December 16 (Day of admission)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
December 22
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
December 28
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
POD 1
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
POD 2
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
POD 4
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
POD 6
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
POD 7
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Reference range
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Hb (g/dL) & 7.0 & 7.6 & 10.2 & 9.6 & 7.6 & 8.6 & 10.0 & 10.0 &
12.0-15.0 \\
HCT (\%) & 23.0 & 23.5 & 33.1 & 20.0 & 21.8 & 26.8 & 30.8 & - & 36-46 \\
Platelets (/µL) & 128,000 & 97,000 & 129,000 & 218,000 & 104,000 &
75,000 & 64,000 & 64,000 & 150,000--410,000 \\
PT (seconds) & - & - & 12.4 & 40.70 & - & - & 17.7 & - & 11.7--15.3 \\
aPTT (seconds) & - & - & - & - & - & - & 48.90 & - & 26-40 \\
Fibrinogen (g/L) & - & - & - & - & - & 1.4 & - & - & 2.00-4.00 \\
D-dimer (µg/mL FEU) & - & - & - & - & - & 35.2 & - & - & 0-0.55 \\
Total bilirubin (mg/dL) & - & - & - & 2.8 & 1.8 & - & 1.4 & - &
1.8-3.5 \\
ALP (IU/L) & - & - & - & 135 & 115 & - & 108 & - & 34--104 \\
LDH (IU/L) & - & 454 & - & 424 & 357 & - & 449 & - & 140--271 \\
BUN (mg/dL) & - & - & - & - & - & - & 24 & - & 5--23 \\
Serum creatinine (mg/dL) & - & - & 0.35 & - & - & 0.30 & - & - &
0.6--1.2 \\
\end{longtable}

POD: Post operative day, Hb: Hemoglobin, HTC: Hematocrit, PT:
Prothrombin time, aPTT: Activated partial thromboplastin time, ALP:
Alkaline phosphatase, LDH : Lactate dehydrogenase, BUN: Blood Urea
Nitrogen.

\section{Review of literature}\label{review-of-literature}

We searched MEDLINE, Embase, and Scopus. Only three cases of KTS
complicated with KMS in pregnancy have been reported, reflecting the
rarity of this condition. KTS was diagnosed prior to pregnancy in two
cases, while it was misdiagnosed as acromegaly and only identified
during the last trimester in the third {[}9{]}. All cases had the
typical clinical findings of KTS, including multiple varicosities at
different sites, hypertrophy, and hemangiomas, with one case also
showing port-wine stains {[}9{]}. Postpartum laboratory findings failed
to improve despite treatment suggesting refractory coagulopathy which is
consistent with KMS. All cases involved vulval varicosities that
necessitated cesarean delivery, with profuse bleeding occurring either
during or after the operation and requiring multiple transfusions. All
were managed with a multidisciplinary approach and received
anticoagulants and transfusions, with two requiring massive
transfusion{[}7,9{]}, other lines of treatment included corticosteroids
and antifibrinolytics{[}7,8{]}. One patient required postpartum
hysterectomy due to life-threatening hemorrhage, along with other severe
complications including DIC, sepsis, peritonitis, and hemoperitoneum
requiring emergency laparotomy {[}9{]}. All required prolonged post op
hospital admission. None of the neonates showed evidence of KTS.
Detailed summary of the three cases is shown in Table~\ref{tbl-3}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.1667}}
  >{\raggedright\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.1667}}
  >{\raggedright\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.1667}}
  >{\raggedright\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.1667}}
  >{\raggedright\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.1667}}
  >{\raggedright\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.1667}}@{}}
\caption{}\label{tbl-3}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Author (Year)}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Presentation}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Key Clinical Features}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{KMS / Labs}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Management}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Outcome}
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Author (Year)}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Presentation}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Key Clinical Features}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{KMS / Labs}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Management}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Outcome}
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
\textbf{Neubert (1995)} & 22 y, primigravida, 37 wks (known KTS) &
Hemangiomas, limb hypertrophy, massive vulvovaginal varicosities &
Post-op KMS: thrombocytopenia, ↓ fibrinogen, ↑ PT/PTT, ↑ fibrin split
products & CS at 39 wks; hematoma evacuation; ICU; transfusion; heparin
+ aminocaproic acid & Discharged day 20; healthy neonate \\
\textbf{Kanmani (2021)} & 24 y, primigravida, 29 wks (known KTS),
bleeding gums & Limb hypertrophy, varicosities (vulval, lower limb) &
Antenatal KMS: severe thrombocytopenia (limited labs reported) &
Steroids + platelet transfusion; CS at 35 wks; post-op anticoagulation +
steroids & Discharged day 20; healthy neonate \\
\textbf{Zhang (2019)} & 26 y, KTS diagnosed in 3rd trimester; severe
postpartum bleeding & Hemodynamic instability, ecchymoses, massive limb
hypertrophy, varicosities & Post-op KMS: thrombocytopenia, ↓ fibrinogen,
↑ PT/APTT, ↑ FDP, ↑ D-dimer & CS at 39 wks; hysterectomy; embolization;
laparotomy; anticoagulation & Discharged day 42; healthy neonate \\
\end{longtable}

\section{Discussion}\label{discussion}

The occurrence of KTS complicated by KMS during pregnancy is extremely
rare, and, to our knowledge, only three cases have been reported.
{[}7--9{]}

Klippel-Trenaunay Syndrome (KTS), also referred to as
capillary-lymphatic-venous malformation (CLVM), is characterized by
capillary malformations, soft tissue or bony hypertrophy, and varicose
veins or venous malformations. The presence of at least two of these
features suggests the diagnosis, which is supported by imaging. Magnetic
resonance imaging, Color Doppler studies, and pelviabdominal ultrasounds
may all be used to visualize vascular malformations associated with
KTS.{[}10{]}

Its hallmark features predominantly affect one lower limb (85\%) causing
a discrepancy in limb length, although bilateral involvement may occur
in a minority of cases (12.5\%). However, it is a generalized disorder
and can involve multiple body regions including the pelvis, abdomen,
head and neck, as well as back, pelvis, and bladder as in our case.
Capillary malformations are the most common presentation (98\%),
followed by varicosities or venous malformations (72\%), and limb
hypertrophy (67\%) {[}11{]}.

Morbidity in KTS primarily arises from an increased risk of venous
insufficiency, thromboembolism, and hemorrhage. Pregnancy may further
aggravate these risks, although evidence regarding pregnancy outcomes
and optimal management remains limited. A cross-sectional study of sixty
adult women with KTS reported increased risks of pregnancy-associated
deep vein thrombosis, pulmonary embolism, and severe postpartum
hemorrhage compared with the general population, with nearly half the
patients also experiencing exacerbation of KTS-related symptoms{[}12{]}.
In contrast, another study comparing pregnant women with KTS versus
nulligravid women with KTS found no difference in bleeding or
thromboembolic risk, although a limitation was the possibility of women
with more severe KTS being discouraged from pregnancy {[}13{]}.

Fetal complications, including intrauterine growth restriction (IUGR),
were reported in a few cases, including our case. However, no
significant fetal effects were reported in the majority of patients with
KTS, indicating that its impact on fetal development is generally
limited.{[}14{]}

Patients may present with a wide variety of manifestations either
primary or due to complications such as pain, bleeding, cellulitis,
massive vaginal bleeding, visceral bleeding, and bleeding gums, and
other vascular complications such as severe hematuria and hematochezia
(fewer than 5\%). Our case presented with clinically significant
hematuria. Other less common but serious manifestations include deep
vein thrombosis (5.8\%), pulmonary embolism (2.3\%), severe PPH (11\%),
and potential preeclampsia. {[}14,15{]}

Kasabach-Merritt Syndrome (KMS), a rare but life-threatening
complication, is characterized by thrombocytopenia, microangiopathic
hemolytic anemia, and consumptive coagulopathy in the presence of a
vascular tumor {[}16{]}. Patients commonly present with persistent
bleeding and thrombocytopenia refractory to blood products. Our patient
developed post-op hematoma and hemoperitoneum which was managed
conservatively with success. Specific therapy was initiated once
Kasabach-Merritt syndrome was suspected and the patient eventually made
a complete recovery. The prompt recognition and initiation of therapy
are critical to reduce mortality in KMS. Delayed recognition was
associated with more complicated clinical courses, as in the KTS patient
at 39 weeks who was not previously diagnosed with KTS, and did not
receive LMWH, losing 1500 mL of blood of post-op and 4500mL of blood
through vaginal bleeding on day 10 postpartum, necessitating a
hysterectomy and abdominal gauze packing.{[}9{]}

Diagnosis of KMS is confirmed by lab findings of thrombocytopenia,
hypofibrinogenemia, elevated D-dimer, and prolonged coagulation times.
The absence of thrombocytopenia may indicate refractory coagulopathy
rather than KMS, although atypical presentations should be suspected in
presence of hemangiomas.{[}15{]}

The management of KTS becomes more complex when complicated by Kasabach
Merritt syndrome (KMS). Imaging studies are crucial for assessing the
extent of vascular malformations near the spinal cord and pelvic
structures, with MRI being the preferred imaging modality for accurately
evaluating lesions size, extent, and anatomical involvement which is
critical for planning the anesthesia and delivery type. Doppler
ultrasound is effective for diagnosing venous malformations. Regular
maternal and fetal assessment is essential due to risk of placental
involvement {[}17,18{]}. Our patient underwent first-trimester
ultrasound and MRI at 30 weeks. MRI demonstrated extensive venous
malformations involving the pelvic, perivesical, perineal, gluteal,
thigh, and anterior abdominal regions. Ultrasound revealed
hepatosplenomegaly, soft tissue lesions in the urinary bladder,
bilateral refluxing parametrial venous channels, and no evidence of deep
vein thrombosis.

Deciding the mode of delivery in a pregnant woman with KTS requires a
multidisciplinary team (MDT). In most reported cases, cesarean section
was opted for due to the presence of vulval varicosities.{[}19{]} In our
case, emergency cesarean section under general anesthesia was
recommended by an MDT involving obstetrics, hematology, anesthesia, and
neonatology due to both fetal and maternal risks. Vertical midline
abdominal incision revealed significant varicosities in the anterior
abdominal wall, over the lower uterine segment, and in the interface
between the uterus and the bladder. Comprehensive preparations were made
before and after delivery, including the administration of tranexamic
acid and LMWH.

Prophylactic anticoagulation with LMWH should be considered during
pregnancy period given the elevated risk of VTE {[}20{]}, with regular
coagulopathy monitoring and Imaging. Postpartum management may involve
anticoagulation, platelet transfusion, cryoprecipitate, fresh frozen
plasma and antifibrinolytic agents such as TXA. Postpartum follow up is
essential as KMS can develop or worsen after delivery and they may
require large volumes of blood products to manage the ongoing
coagulopathy, but typically remain refractory, showing minimal to no
improvement. {[}12{]}

\section{Conclusion}\label{conclusion}

Pregnancy in women with Klippel--Trenaunay syndrome complicated by
Kasabach--Merritt syndrome is extremely rare and posing significant
diagnostic challenges. Early suspicion and diagnosis with intensive
antenatal surveillance and multidisciplinary management are crucial to
navigate the complex balance between thrombosis and bleeding and to
optimize maternal and perinatal outcomes in such high risk cases.

\section{Abbreviation}\label{abbreviation}

Klippel-Trenaunay syndrome (KTS)

Kasabach Meritt Syndrome (KMS)

Magnetic resonance imaging (MRI)

Ultrasonography (US)

Transvaginal ultrasound (TVUS)

Intensive care unit (ICU)

Low-molecular-weight heparin (LMWH)

Lactate dehydrogenase (LDH)

Blood Urea Nitrogen (BUN)

Prothrombin time (PT)

Partial Thromboplastin Time (PTT)

Complete blood picture (CBC)

Disseminated Intravascular Coagulation (DIC)

Multidisciplinary team (MDT)

\section{Declarations}\label{declarations}

\subsection{Ethics approval and consent to
participate}\label{ethics-approval-and-consent-to-participate}

Not applicable.

\subsection{Consent for publication}\label{consent-for-publication}

A written consent for publication has been obtained from the patient.

\subsection{Availability of data and
materials}\label{availability-of-data-and-materials}

The data and materials supporting the conclusions of this article are
available as a supplementary materials.

\subsection{Competing interests}\label{competing-interests}

The authors declare that they have no competing interests.

\subsection{Funding}\label{funding}

This research received no specific grant from any funding agency in the
public, commercial or not-for-profit sectors.

\subsection{Authors' contributions}\label{authors-contributions}

SIA, ME, AFN contributed to writing the first draft of the manuscript.
All the authors revised the manuscript critically for important
intellectual content. All authors approved the final version of the
manuscript.

\subsection{Acknowledgements}\label{acknowledgements}

We sincerely thank the healthcare providers at Ain Shams University
Hospital of Obstetrics and Gynecology for their dedication and
commitment to patient care in the operating room. We deeply appreciate
their contributions and the valuable role they play in ensuring
high-quality surgical care.

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\phantomsection\label{refs}
\begin{CSLReferences}{0}{1}
\bibitem[\citeproctext]{ref-ISSVA2018}
1. International Society for the Study of Vascular Anomalies. {ISSVA
Classification for Vascular Anomalies}.
\url{https://www.issva.org/UserFiles/file/ISSVA-Classification-2018.pdf};
2018.

\bibitem[\citeproctext]{ref-Pavone2023}
2. Pavone P, Marino L, Cacciaguerra G, Di Nora A, Parano E, Musumeci G,
et al. \href{https://doi.org/10.3390/children10081421}{Klippel-trenaunay
syndrome, segmental/focal overgrowth malformations: A review}. Children
(Basel). 2023;10:1421.

\bibitem[\citeproctext]{ref-mckusick1963}
3. McKusick VA. Frederick Parkes Weber{\textemdash}1863-1962. JAMA
{[}Internet{]}. 1963;183. Available from:
\url{http://dx.doi.org/10.1001/jama.1963.63700010018015}

\bibitem[\citeproctext]{ref-sikova1999}
4. Sikova DVD, Pavlova LjT, Laskoska MTV, Nikolovska ST, Biljanovska NC.
Naevus varicosus osteohypertrophicus. Springer US; 1999. p. 535--40.
Available from: \url{http://dx.doi.org/10.1007/978-1-4615-4857-7_80}

\bibitem[\citeproctext]{ref-Blei2024}
5. Blei F. {Klippel-Trenaunay Syndrome: Clinical Manifestations,
Diagnosis, and Management}. UpToDate.
\url{https://www.uptodate.com/contents/klippel-trenaunay-syndrome-clinical-manifestations-diagnosis-and-management};
2024.

\bibitem[\citeproctext]{ref-Tian2026}
6. Tian Y, Yuan Y, Wei L, Xu Z, Li L, Li L.
\href{https://doi.org/10.1002/ped4.70041}{Kaposiform
hemangioendothelioma: Diagnosis and treatment}. Pediatric Investigation.
2026;

\bibitem[\citeproctext]{ref-Neubert1995}
7. Neubert GA, Golden MA, Rose NC.
\href{https://doi.org/10.1016/0029-7844(94)00349-I}{Kasabach-merritt
coagulopathy complicating klippel-trenaunay-weber syndrome in
pregnancy}. Obstetrics \& Gynecology. 1995;85:831--3.

\bibitem[\citeproctext]{ref-Kanmani2021}
8. Kanmani K, Meena M, Narmadha D, A. GV.
\href{https://doi.org/10.18203/2320-1770.ijrcog20211511}{Klippel
trenaunay syndrome--an obstetric challenge}. International Journal of
Reproduction, Contraception, Obstetrics and Gynecology. 2021;10:2081--4.

\bibitem[\citeproctext]{ref-zhang2019}
9. Zhang J, Wang K, Mei J. Late puerperal hemorrhage of a patient with
Klippel{\textendash}Trenaunay syndrome. Medicine {[}Internet{]}.
2019;98:e18378. Available from:
\url{http://dx.doi.org/10.1097/MD.0000000000018378}

\bibitem[\citeproctext]{ref-horbach2017}
10. Horbach S, Lokhorst M, Oduber C, Middeldorp S, Post J van der, Horst
C van der. Complications of pregnancy and labour in women with
Klippel{\textendash}Trénaunay syndrome: a nationwide cross{-}sectional
study. BJOG: An International Journal of Obstetrics \& Gynaecology
{[}Internet{]}. 2017;124:1780--8. Available from:
\url{http://dx.doi.org/10.1111/1471-0528.14698}

\bibitem[\citeproctext]{ref-Jacob1998}
11. Jacob AG, Driscoll DJ, Shaughnessy WJ, Stanson AW, Clay RP,
Gloviczki P. Klippel-Trénaunay Syndrome: Spectrum and Management. Mayo
Clinic Proceedings {[}Internet{]}. 1998;73:28--36. Available from:
\url{http://dx.doi.org/10.1016/S0025-6196(11)63615-X}

\bibitem[\citeproctext]{ref-silvacorreia2024}
12. Silva Correia IF, Hussain M, Johnson J-A. Obstetric management for
pregnant women with Klippel{\textendash}Trenaunay syndrome: A UK case
report and review of the literature. International Journal of Gynecology
\& Obstetrics {[}Internet{]}. 2024;168:484--6. Available from:
\url{http://dx.doi.org/10.1002/ijgo.15889}

\bibitem[\citeproctext]{ref-Marvin2019}
13. Marvin EK, Schoch JJ, Nguyen H, Anderson KR, Driscoll DJ, Rose CH,
et al. Venous thromboembolic and bleeding complications among pregnant
women with Klippel-Trenaunay syndrome. Journal of the American Academy
of Dermatology {[}Internet{]}. 2019;81:1277--82. Available from:
\url{http://dx.doi.org/10.1016/j.jaad.2019.04.018}

\bibitem[\citeproctext]{ref-Akay2025}
14. Akay E, Uzun Gül AD, Türkoğlu A.
\href{https://doi.org/10.1186/s12884-025-07540-0}{Recurrent preeclampsia
in a pregnant woman with klippel-trenaunay syndrome: Two cesarean
deliveries and multiple extremity involvement -- case report and
literature review}. BMC Pregnancy and Childbirth. 2025;25:407.

\bibitem[\citeproctext]{ref-Chang2025}
15. Chang R, Zhang J, Zhang F, Wen L, Jiang Y. Pregnancy in Women With
Klippel{\textendash}Trenaunay Syndrome Complicated by Uterine Vascular
Malformation: A Case Report and Literature Review. Cureus
{[}Internet{]}. 2025; Available from:
\url{http://dx.doi.org/10.7759/cureus.90065}

\bibitem[\citeproctext]{ref-Mahajan2017}
16. Mahajan P, Margolin J, Iacobas I. Kasabach-Merritt Phenomenon:
Classic Presentation and Management Options. Clinical Medicine Insights:
Blood Disorders {[}Internet{]}. 2017;10:1179545X1769984. Available from:
\url{http://dx.doi.org/10.1177/1179545X17699849}

\bibitem[\citeproctext]{ref-Howlett1994}
17. Howlett DC, Roebuck DJ, Frazer CK, Ayers B. The use of ultrasound in
the venous assessment of lower limb Klippel-Trenaunay syndrome. European
Journal of Radiology {[}Internet{]}. 1994;18:224--6. Available from:
\url{http://dx.doi.org/10.1016/0720-048x(94)90340-9}

\bibitem[\citeproctext]{ref-Asghar2020}
18. Asghar F, Aqeel R, Farooque U, Haq A, Taimur M. Presentation and
Management of Klippel-Trenaunay Syndrome: A Review of Available Data.
Cureus {[}Internet{]}. 2020; Available from:
\url{http://dx.doi.org/10.7759/cureus.8023}

\bibitem[\citeproctext]{ref-Keepanasseril2017}
19. Keepanasseril A, Keerthana K, Keepanasseril A, Maurya DK, Kadambari
D, Sistla S. Pregnancy in women with Klippel-Trenaunay syndrome: Report
of three pregnancies in a single patient and review of literature.
Obstetric Medicine {[}Internet{]}. 2017;10:177--82. Available from:
\url{http://dx.doi.org/10.1177/1753495X17719181}

\bibitem[\citeproctext]{ref-marvin2019}
20. Marvin EK, Schoch JJ, Nguyen H, Anderson KR, Driscoll DJ, Rose CH,
et al. Venous thromboembolic and bleeding complications among pregnant
women with Klippel-Trenaunay syndrome. Journal of the American Academy
of Dermatology {[}Internet{]}. 2019;81:1277--82. Available from:
\url{http://dx.doi.org/10.1016/j.jaad.2019.04.018}

\end{CSLReferences}




\end{document}
